Visualization of [fulle name] Fractional Integrals

### 2019-04-30 fractional/CMJ style files/article-template.tex
made good progress on paper

The area associated with the regions depicted in Fig. are plotted in Fig using circular markers. The circular marker is depicted in Figure using the same tint-of-gray

>>>>

If we evaluate the integral in Eq for all $\alpha\in \mathsf{A}$ we obtain the curves in the left-most column of Table.... These curves are depicted in Fig.
The area of the regions depicted in Fig are also plotted in Fig using circular markers. As expected, the circular markers that correspond to the areas of the regions 
from a particular choice of $\alpha$ (i.e. from a particular panel of Fig) in Fig lie on the curve in Fig that is associated with the same choice of $alpha$. Moreover, note that we have adopted the 
same color scheme in Fig and Fig. Using the same color scheme in both Figures makes it clear which of the area values in Fig can be associated with which regions in Fig.

The circular markers in Figure ?? is depicted using the same tint-of-gray with which the right edge of the region  in question is depicted in Fig.

Each of the curves 
in Fig can therefore be associated with one of the panels in Fig. The area associated with the regions depicted in each of the panels in Fig. are plotted on the curves 
in 
associated with a particular panel appropriate 
curves 
in Fig using circular markers. The circular marker is depicted in Figure using the same tint-of-gray with which the 
right edge of the region in question is depicted in Fig.
